---
title: "Analysis of International Education Costs vs. University Rankings"
author: 
 - name: "Girika"
 - name: "Catherine"
 - name: "Chang Heng-Hsieh"
format: 
  pdf: default
toc: true
---

## Executive Summary

This study investigates the relationship between actual study abroad costs and international university rankings. We compare academic achievement with financial affordability across major study destinations using data from the 2024 and 2025 QS World University Rankings and international education cost datasets. The analysis focuses on master's degree programs in the top 10 QS ranking countries, examining tuition, living costs, visa fees, and insurance expenses. The findings reveal significant cost variations among top-ranking countries, providing valuable insights for international students seeking quality education at optimal costs.

## Introduction

The international education sector is growing rapidly, with more students exploring study opportunities beyond their home countries in search of both quality and affordability. The QS World University Rankings serve as a trusted benchmark for comparing institutions across dimensions such as academic reputation, graduate employability, and sustainability. **While top-ranked universities typically involve higher costs, the total expense varies significantly between countries due to differences in living costs, visa requirements, and local economic conditions.** Expenses like tuition, accommodation, visa fees, and insurance can significantly impact overall affordability for international students.

For many prospective students, cost considerations are just as critical as academic quality when making study abroad decisions. Limited research has systematically compared education costs across top-ranking university destinations. This gap in knowledge makes it difficult for students to make informed decisions about cost-effective study options. In this report, we examine both academic performance and financial affordability by merging QS ranking data from 2024 and 2025 with international education cost datasets. Our analysis focuses specifically on master's degree programs in the top 10 countries with the highest QS university rankings. The findings aim to provide practical guidance for international students seeking optimal value in their education investment.

## Methodology

-   **Research Design and Data Sources** This study uses quantitative analysis to compare education costs and university rankings. We combined QS World University Rankings 2024-2025 with Kaggle international education cost dataset. The research focuses on master's degree programs only. As shown in @fig-methodology, we followed a systematic approach from data collection to final analysis, focusing on the top 10 QS ranking countries.

```{r}
#| label: fig-methodology
#| fig-cap: "Research methodology flowchart showing data processing steps"
#| echo: false
#| fig-width: 8
#| fig-height: 6

library(DiagrammeR)
DiagrammeR::grViz("
digraph flowchart {
  node [fontname = Arial, shape = rectangle, style = filled, fillcolor = lightblue, fontsize = 10]
  edge [fontname = Arial]
  
  A [label = 'Merge QS Rankings\\n2024 & 2025 Data']
  B [label = 'Identify Top 10 Countries\\nfrom QS Rankings']
  C [label = 'Filter Kaggle Dataset\\nfor These 10 Countries']
  D [label = 'Select Master\\'s Level\\nPrograms Only']
  E [label = 'Calculate Total Study Cost\\n(Tuition + Rent + Visa + Insurance)']
  
  A -> B -> C -> D -> E
}
")
```

-   **Data Processing Steps** @tbl-processing shows our five-stage data processing method. First, we collected both datasets and checked data quality. Second, we calculated total study cost for each country by adding tuition, rent, visa fees, and insurance. Third, we filtered data to focus on master's level programs. Fourth, we selected the top 10 QS ranking countries. Finally, we cleaned the data and merged both datasets.

```{r}
#| label: tbl-processing
#| tbl-cap: "Data processing stages and R functions used"
#| echo: false

library(knitr)
library(kableExtra)

processing_stages <- data.frame(
  Stage = c("1. Data Merging", "2. Country Selection", "3. Data Filtering", 
            "4. Level Selection", "5. Cost Calculation"),
  Procedure = c("Combine QS 2024 & 2025", "Identify top 10 countries", 
                "Filter Kaggle by countries", "Select master's programs", 
                "Sum all cost components"),
  R_Functions = c("rbind(), bind_rows()", "group_by(), top_n()", 
                  "filter(), %in%", "filter()", "mutate(), rowSums()"),
  Output = c("Merged QS data", "Top 10 countries list", "Country-matched data", 
             "Master's level data", "Total cost dataset")
)

knitr::kable(processing_stages, 
             col.names = c("Stage", "Procedure", "R Functions", "Output"),
             format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

-   **Analysis Methods and Tools** All analysis was done in R using the tidyverse for data processing and ggplot2 for visualization to ensure reproducibility. We calculated basic statistics like averages and standard deviations. We also performed simple correlation analysis to explore the relationship between study costs and QS rankings.

## Results

## Discussion, Conclusion & Recommendations

## References

**Member A- Girika**

-   Sections: **Executive Summary** (max 4 sentences), **Introduction** (max 10 sentences), and **Methodology** (max 300 words with 1 figure + 1 table)

-   Git branch: method (This is quite a heavy section with both writing and visuals — if needed, the rest of us can help with generating or editing the plots/tables.)

**Member B- Chen lie**

-   Section: **Results** (run analysis + create 1 figure or table + 200-word summary of key findings)

-   Git branch: results

**Member C -Jessica**

-   Sections: **Discussion**, **References**, and **Slides** (create a basic slide outline; we’ll each fill in our parts later)

-   Also responsible for helping **merge branches** into main later on

• Git branch: discuss
