---
title: "Cost of International Education"
author: ""
format: 
  pdf: default
toc: true
---

## Executive Summary

## Introduction

## Methodology



## Results
We analyzed the average total cost of studying a Master's program across the top 10 QS-ranked countries. This included tuition, rent, visa fees, and insurance. The goal was to identify how Australia compares with other top destinations in terms of affordability.

### Load and Prepare Data
```{r}
library(dplyr)
library(readr)

# Load data
df <- read_csv("data/cleaned_education_costs.csv")
qs_df <- read_csv("data/top_countries.csv")

# Summarise average cost by country
summary_df <- df %>%
  group_by(Country) %>%
  summarise(
    Avg_Tuition = round(mean(Tuition_USD), 0),
    Avg_Rent = round(mean(Rent_USD * 12 * Duration_Years), 0),
    Avg_Total_Cost = round(mean(Total_Cost_USD), 0),
    .groups = "drop"
  )

# Merge with QS Top 100 counts
merged_df <- left_join(summary_df, qs_df, by = "Country")
```








### Table 1: Country Ranking by Total Study Cost
```{r}
kable(merged_df[order(merged_df$Avg_Total_Cost), ],
      caption = "Table: Country Ranking by Total Study Cost and QS Top 100 Count")
```
As seen in Table 1, Australia ranks second highest in total study cost, placing it among the least affordable destinations for international Master’s students. This contrasts with more cost-effective options like South Korea, Germany, and China.



### Figure 1: Bar Chart of Total Cost by Country
```{r}
ggplot(merged_df, aes(x = reorder(Country, Avg_Total_Cost), y = Avg_Total_Cost)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(
    title = "Average Total Study Cost by Country",
    x = "Country",
    y = "Average Total Cost (USD)"
  ) +
  theme_minimal()
```

Figure 1 visually highlights this cost gap between Australia and other countries in the dataset. The results suggest that while Australia is a popular and prestigious education destination, it comes with a relatively high financial burden compared to similarly ranked alternatives.


We analyzed the average total cost of studying a Master's degree across the top-ranking QS countries. As shown in Table 1, the United States had the highest average cost (approximately $100,200), followed by Australia ($70,477) and the United Kingdom ($57,381). In contrast, countries like South Korea, Germany, and China offered significantly lower total costs, all under $30,000.

Figure 1 visualizes the variation in cost across countries. Interestingly, some countries with strong QS representation — such as Australia (18 Top 100 universities) — are also among the most expensive. However, South Korea, with 10 QS-ranked institutions, maintains the lowest average cost in the dataset.

These results highlight the trade-offs between academic prestige and affordability. While top-ranked destinations offer global recognition, the financial burden varies widely and may impact students’ decision-making.





## Discussion, Conclusion & Recommendations

## References

**Member B- Chen lie**

-   Section: **Results** (run analysis + create 1 figure or table + 200-word summary of key findings)

-   Git branch: results

