---
title: "ANALYSIS OF INTERNATIONAL EDUCATION COSTS vs. UNIVERSITY RANKINGS "
format: 
  revealjs:
    theme: solarized
    slide-number: true
    transition: slide
editor: visual
---

------------------------------------------------------------------------

## Problem Introduction

- 🌍 **Growing Global Mobility**: 
International education sector expanding rapidly

- 💰 **Quality vs Affordability Dilemma**: 
Costs vary a lot between countries, and students seek both academic excellence and financial feasibility

- 📊 **Information Gap**:  
Limited systematic comparison of education costs across top-ranking university destinations

---

**Key Questions**

- ❓ Do top QSrankings (higher academic quality) = higher costs?
- ❓ Which countries offer best value for international students?
- 🎯 Goal: Compare study cost vs. QS ranking to find cost-effective options

------------------------------------------------------------------------

## Dataset Description
#### Data Sources:

- **QS World University Rankings 2024-2025:**

🎓 Academic reputation, graduate employability, sustainability metrics
🎓 Global benchmark for university comparison

- **Kaggle: International Education Cost Dataset:**

💸 Comprehensive cost breakdown by country
💸 Includes Tuition + Living + Visa + Insurance


#### Focus:

**Academic Level**: 
- `Master's degree programs only`
- Standardized comparison across countries

**Geographic Scope:**
- Top 10 countries with the highest QS ranking
- Global coverage of major study destinations

**Time Frame:**
- QS Rankings: 2024-2025 academic yearr


------------------------------------------------------------------------

## Method
#### Analysis Processing Flowchart

```{r}

#| label: fig-methodology
#| fig-cap: "Research methodology flowchart showing data processing steps"
#| echo: false
#| fig-width: 8
#| fig-height: 6

library(DiagrammeR)
DiagrammeR::grViz("
digraph flowchart {
  node [fontname = Arial, shape = rectangle, style = filled, fillcolor = lightblue, fontsize = 10]
  edge [fontname = Arial]
  
  A [label = 'Merge QS Rankings\\n2024 & 2025 Data']
  B [label = 'Identify Top 10 Countries\\nfrom QS Rankings']
  C [label = 'Filter Kaggle Dataset\\nfor These 10 Countries']
  D [label = 'Select Master\\'s Level\\nPrograms Only']
  E [label = 'Calculate Total Study Cost\\n(Tuition + Rent + Visa + Insurance)']
  
  A -> B -> C -> D -> E
}
")
```

#### Data Processing Steps

In this section, I’ll walk you through how we processed the data before performing our analysis. As shown in the table, our workflow followed five main steps: 1.⁠ ⁠Merged QS 2024 and 2025 rankings 2.⁠ ⁠Identified top 10 countries by QS Top 100 presence 3.⁠ ⁠Filtered Kaggle dataset for these countries 4.⁠ ⁠Focused on Master’s level programs 5.⁠ ⁠Calculated total study cost (Tuition + Rent + Visa + Insurance)

We used R functions like filter(), mutate(), and rowSums() to clean and summarize the data.
```{r}
#| label: tbl-processing 
#| tbl-cap: "Data processing stages and R functions used" 
#| echo: false

library(knitr) library(kableExtra)

processing_stages \<- data.frame( Stage = c("1. Data Merging", "2. Country Selection", "3. Data Filtering", "4. Level Selection", "5. Cost Calculation"), Procedure = c("Combine QS 2024 & 2025", "Identify top 10 countries", "Filter Kaggle by countries", "Select master's programs", "Sum all cost components"), R_Functions = c("rbind(), bind_rows()", "group_by(), top_n()", "filter(), %in%", "filter()", "mutate(), rowSums()"), Output = c("Merged QS data", "Top 10 countries list", "Country-matched data", "Master's level data", "Total cost dataset") )

knitr::kable(processing_stages, col.names = c("Stage", "Procedure", "R Functions", "Output"), format = "html") %\>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

------------------------------------------------------------------------

### Analysis Tools & Techniques

⁠ markdown \## Analysis Tools & Techniques

-   Analysis performed using **R** and Quarto for full reproducibility\
-   Used `tidyverse` for data processing and cleaning\
-   Created visualizations using `ggplot2`\
-   Calculated averages for tuition, rent, and total study cost per country\
-   Performed simple correlation analysis between costs and QS rankings

Results – Cost Comparison Table \## Results – Study Cost Rankings

We analyzed the average total cost of studying a Master's degree across the top QS-ranked countries. This includes tuition, rent, visa fees, and insurance.

 ⁠{r} kable(merged_df\[order(merged_df\$Avg_Total_Cost), \], caption = "Table 1: Total Study Cost and QS Top 100 Count by Country")

⁠ • 🇺🇸 United States: Highest cost (\~USD 100,200)

• 🇦🇺 Australia: Second highest (\~USD 70,477)

• 🇰🇷 South Korea: Lowest average cost

• Lower-cost countries (Germany, China) also have strong QS presence

------------------------------------------------------------------------

### Results – Bar Chart of Costs

 ⁠markdown \## Results – Visual Comparison

⁠ {r} ggplot(merged_df, aes(x = reorder(Country, Avg_Total_Cost), y = Avg_Total_Cost)) + geom_bar(stat = "identity", fill = "skyblue") + labs( title = "Figure 1: Average Total Study Cost by Country", x = "Country", y = "Avg Total Cost (USD)" ) + theme_minimal()  ⁠ Australia and the US are among the most expensive destinations, while South Korea, Germany, and China offer affordability with quality. This highlights a trade-off between academic prestige and financial accessibility.

------------------------------------------------------------------------

## Discussion

-   Our findings show that **academic prestige doesn’t guarantee affordability**.

-   Countries like the **US (\~\$100,200)** and **Australia (\~\$70,500)** have many top QS-ranked universities but also **very high study costs**.

-   On the other hand, **South Korea (\~\$22,800)**, **Germany (\~\$24,900)**, and **China (\~\$28,300)** offer **much lower costs** while maintaining QS presence.

-   These patterns reflect how **national policies**, such as Germany’s free public university system, play a key role in affordability.

-   This proves that students can access **quality education without breaking the bank**.

------------------------------------------------------------------------

## Study Limitations

-   We used **average country-level costs**, which may not reflect variation between cities or universities.
-   **Scholarships and grants** were not considered, yet these can significantly lower actual costs.
-   **Exchange rates** fluctuate over time, which could impact affordability.
-   Language, cultural preferences, and long-term goals (e.g., migration, job prospects) were also **not included**, though they’re critical for many students.

------------------------------------------------------------------------

## Conclusion & Recommendations

🧠 **Conclusion** - No direct link between QS rank and affordability. - Students can find **excellent education at lower costs** in countries like South Korea, Germany, and China. - **Affordability and quality must be balanced** when choosing a destination.

✅ **Recommendations** - **Students**: Look beyond rankings — evaluate total cost of attendance. - **Institutions & policymakers**: Be more transparent; offer **more financial support**. - **Future researchers**: Include job outcomes, immigration pathways, and scholarships for a full picture.
